The Array of Long-Baseline Antennas for Taking Radio Observations from the Sub-Antarctic

### 2020-04-01 albatros_paper.tex
HCC: added new ALBATROS 2-element schematic
HCC fixed duplicate text in 2-element figure
HCC overhauled intro, working on pathfinder text

@@

\markboth{Author's Name}{Paper Title}

@@

\keywords{Keyword 1; keyword 2; keyword 3.}

@@

Measurements of redshifted \SI{21}{\cm} emission of neutral hydrogen
across a wide range of radio frequencies have the potential to
elucidate the universe's history from the cosmic ``dark ages'' up to
the formation of large-scale structures (see,
e.g.,~\citep{ska_physics,2013PhRvD..87d3002L,2014ApJ...782...66P}.
The dark ages, which occurred after recombination and correspond to a
period when the universe was filled with neutral hydrogen, are
unexplored to date and represent one of the final observational
frontiers in cosmology.  This epoch contains a potential wealth of
cosmological information~\citep{loeb_zaldarriaga}, but the required
redshifted frequencies of $\lesssim 30$~MHz are exceptionally
difficult to observe.  The primary challenges include Galactic
foreground emission, ionospheric interference, and terrestrial
radio-frequency interference (RFI). \\

% At the very lowest frequencies, the state of the art among
% ground-based measurements dates from the 1950s, when Reber and Ellis
% caught brief glimpses of the $\sim 2$~MHz sky at low
% resolution~\citep{reber}.  The lowest frequency to date for
% high-resolution sky imaging has been achieved by the LWA, which
% reported observations at 36.5~MHz using only 28 hours of
% data~\citep{lwa}.  Preliminary observations from Marion Island
% (\S\ref{s:dark_method}) suggest that despite the present-day RFI
% environment, low-frequency observations may still be accessible from
% carefully selected locations and with new technology developments.

Comprehensive reviews of experimental efforts exist elsewhere but none of them have made measurements at the lowest frequencies of $\lessapprox$ \SI{30}{\MHz}. This is due to the challenges namely, the ionospheric effects, radio frequency intereference (RFI), Galactic emission and instrumental systematics which is non transparent below \SI{10}{\MHz} \cite{2019JAI.....850004P}. Two of these experiments represent the lowest frequencies measured to date (Reber’s antenna, RAE-2), and the other two represent the highest resolutions achieved in this frequency range (DRAO, OVRO-LWA).\\

Grote Reber came up with the state of art by constructing a telescope which operated at very low frequencies between 0.52 MHz and 2.1 MHz, which had 192 dipoles. At \SI{2.1}{\MHz} it had a resolution of as low as $\approx$ 5 \degree. The key map of the sky was created by this experiment at \SI{2.1}{\MHz}. He also mentioned that his measurements were influenced by galactic emission and the ionosphere \cite{article, 1988A&A...195..372W}. The Radio Astronomoy Explorer-2 (RAE-2) have very low operating frequency ranges between \SIrange{0.025}{13}{\MHz}, it main science goal was to do radio astronomy evaluation of our Galaxy (the Milkyway), the Sun and all the planets including Earth. The resolution of this experiment is $\approx$ 10 \degree at \SI{4.7}{\MHz} \cite{1975A&A....40..365A}. Both of these experiments made very low resolution measurements.\\

The experiments which made the high resolution measurements are the  Dominion Radio Astrophysical Observatory (DRAO) \SI{22}{\MHz} telescope and the OVRO-LWA \SI{36}{\MHz} experiment. The DRAO telescope operated at \SI{22}{\MHz} and its resolution ranges between $\approx$ \SIrange{1.1}{1.7}{\degree}. Its main science goal was to measure the emission from discrete sources and to observe our Galaxy's emission from its environment \cite{1999A&AS..137....7R}. The OVRO-LWA operates at frequency ranges of 36.528 MHz and 73.152 MHz. At these frequencies it has an angular resolution of \SI{15}{\arcminute} \cite{2018AJ....156...32E}. ALBATROS aims at attempting to do high resolution measurements at a frequency of $<$20 MHz which do not yet exist.\\

Measurements of the radio sky at $\approx$ 100 MHz and below have the capability of unlocking the new observational window in the history of the universe. At the lowest frequencies (tens of MHz), subsequent observations may permit us to probe the cosmic "dark ages," one day, which is an epoch that is obscure to date \cite{2019arXiv190710853C, 2019arXiv190804296K}. This paper will describe a new project that aims to map the low-frequency sky from Marion island using an array of autonomous antenna stations. The final array will consist of  $\approx$ 10 antennas operating at 1.2-81 MHz with baselines up to 20 km. A two-element pathfinder was deployed in April 2018, the first autonomous station was deployed in April 2019 and there'll be discussion of the preliminary observations and upcoming hardware development plans.

\section{Overview of the Instrument}

The ALBATROS-EGG is a two element inteferometer which is making exploratory measurements at a frequency range of \SI{1.2}{MHz}- \SI{81}{MHz} separated by a baseline of \SI{110}{m} as shown in \autoref{Fig:ALBATROS-EGG}. It was deployed in Marion Island in April 2018. Its schematic is shown in \autoref{Fig:ALBATROS-EGG Schematic}. The system uses the dual polarisation dipole like antennas which are omidirectional patterned. The front end electonics (FEE) are configured in a printed circuit board (PCB) which makes it easy for them to be mounted on the supporting structure of the antennas. From the FEE PCB, a coaxial cable sends the signal through to the bias tee which extracts both the RF and the DC without any degradation. \\

The high pass and the low pass filter rejects the low frequency signals and high frequency signals respectively. The signal is then amplified by a $\approx$20 dB amplifier which then send the amplified signals to the Smart Network ADC Processor (SNAP) board which does the readouts and does a series of processing step. The raspberry pi interacts with the SNAP board for data storage.\\

\begin{figure}[h!]
	\begin{center}
		\includegraphics[width=0.55\linewidth]{Figures/ALBATROS-EGG-Schematic.PNG}
		\caption{ALBATROS - EGG pathfinder schematic which consists of the dual polarisation antennas, the 35 dB gain FEE, the 100 m coaxial cable which connects the FEE to the back end Faraday cage which comprises of the bias tee, HPF, LPF, amplifier, snap board and regulated voltage outputs which are powered by 12 VDC batteries.}
		\label{Fig:ALBATROS-EGG Schematic}
	\end{center}
\end{figure}

	\begin{figure}[h]
		\begin{center}
			\includegraphics[width=0.7\linewidth]{Figures/ALBATROS-EGG.PNG}
			\caption{The ALBATROS-EGG pathfinder on Marion Island. The pathfinder comprises two dual-polarization antennas separated by roughly 110 m on an east-west baseline. Long coaxial cables connect the antennas to	an orange shipping container that houses the readout electronics and serves as our "command module".}
			\label{Fig:ALBATROS-EGG}
		\end{center}
	\end{figure}

>>>>

% Define stuff here
\def\albatros{ALBATROS}

@@

\markboth{Author's Name}{ALBATROS instrument}

@@

\keywords{cosmology: observations; dark ages; instrumentation: interferometers}

@@

Measurements of redshifted \SI{21}{\cm} emission of neutral hydrogen
across a wide range of radio frequencies have the potential to
elucidate the universe's history from the cosmic ``dark ages'' up to
the formation of large-scale structures (see,
e.g.,~\citep{ska_physics,2013PhRvD..87d3002L,2014ApJ...782...66P}.
The dark ages, which occurred after recombination and correspond to a
period when the universe was filled with neutral hydrogen, are
unexplored to date and represent one of the final observational
frontiers in cosmology.  This epoch contains a potential wealth of
cosmological information~\citep{loeb_zaldarriaga, 2019arXiv190710853C,
  2019arXiv190804296K}, but the required redshifted frequencies of
$\lesssim 30$~MHz are exceptionally difficult to observe.  The primary
experimental challenges include Galactic foreground emission,
ionospheric interference, and terrestrial radio-frequency interference
(RFI).

Very few experiments have measured the radio sky at $\lesssim 30$~MHz.
Comprehensive reviews exist elsewhere ({\bf citation?}), and here, we
highlight only a few specific examples.  At the very lowest
frequencies, the state of the art among ground-based measurements
dates from the 1950s, when Reber and Ellis caught brief glimpses of
the $2.1$~MHz sky at $\sim 5$\degree\ resolution, using an array of
192~dipoles~\citep{reber, article, 1988A&A...195..372W}.  A few
space-based missions have also performed measurements at similarly low
frequency ranges; for example, the Radio Astronomy Explorer-2 operated
at \SIrange{0.025}{13}{\MHz} with $\sim 10$\degree\ resolution at
\SI{4.7}{\MHz}~\citep{1975A&A....40..365A}.  Measurements with
resolution finer than few-degree scales exist only at higher
frequencies.  For example, the Dominion Radio Astrophysical
Observatory surveyed the northern sky at \SI{22}{\MHz} with
\SIrange{1.1}{1.7}{\degree} resolution~\citep{1999A&AS..137....7R},
and most recently, the Owens Valley Long Wavelength Array mapped the
sky with \SI{15}{\arcminute} resolution between 36.528~MHz and
73.152~MHz~\citep{2018AJ....156...32E}.  Although this experimental
list is not comprehensive, it does illustrate the dearth of
information about the $\lesssim 30$~MHz sky and the lack of high
resolution measurements at the lowest frequencies.

Preliminary observations from Marion
Island~\citep{2019JAI.....850004P} suggest that despite the
present-day RFI environment, low-frequency observations may still be
accessible from carefully selected locations and with new technology
developments.  In this paper, we present the Array of Long Baseline
Antennas for Taking Radio Observations from the Sub-Antarctic
(\albatros), a new experimental effort that aims to map the
low-frequency sky using an array of autonomous antenna stations.  We
describe the overall instrument design and preliminary measurements
from engineering runs that were performed on Marion Island during
2018--2019.

\section{ALBATROS overview}

{\bf Write text here about the overall final configuration.  Describe
  the site, show synthesized beam, discuss high level system
  requirements (power, data storage, etc).  Include deployment
  schedule and introduce 2-element pathfinder in the following
  section.}

The final array will consist of $\approx$ 10 antennas operating at
1.2-81 MHz with baselines up to 20 km. A two-element pathfinder was
deployed in April 2018, the first autonomous station was deployed in
April 2019.

\section{Two-element pathfinder}

\begin{figure}
  \begin{center}
    \includegraphics[width=0.7\linewidth]{Figures/ALBATROS-EGG.PNG}
    \caption{The two-element \albatros\ pathfinder on Marion Island.
      Two dual-polarization LWA antennas are separated by roughly
      110~m on an east--west baseline. Coaxial cables connect the
      antennas to an orange shipping container that houses the readout
      electronics and serves as our ``command module.''}
    \label{Fig:albatros2}
  \end{center}
\end{figure}

\begin{figure}
  \begin{center}
    \includegraphics[width=1.0\linewidth]{Figures/albatros_2elem_schematic/albatros_2elem_schematic.pdf}
    \caption{Schematic for the two-element \albatros\ pathfinder.
      Signals from two dual-polarzation LWA antennas are amplified by
      front-end active baluns ({\bf citation for FEE}), and 100-m
      coaxial cables connect the antennas to the back-end readout
      electronics, which are housed in a Faraday cage denoted by the
      dashed box.  Each of the four antenna outputs is passed to a
      second-stage electronics chain consisting of a bias tee,
      amplifier, and high- and low-pass filters.  The signals are
      digitized at 250~Msamp/s by a SNAP board, and the on-board FPGA
      is programmed with firmware to perform a full cross-correlation
      of all four inputs.  A Raspberry Pi controls the SNAP board and
      also saves the computed spectra to an SD card.  Power to the
      system is provided by a bank of 12~V batteries and several
      regulated voltage outputs.}
    \label{Fig:albatros2_schem}
  \end{center}
\end{figure}

The ALBATROS-EGG is a two element inteferometer which is making
exploratory measurements at a frequency range of \SI{1.2}{MHz}-
\SI{81}{MHz} separated by a baseline of \SI{110}{m} as shown in
\autoref{Fig:albatros2}. It was deployed in Marion Island in April
2018. Its schematic is shown in \autoref{Fig:albatros2_schem}. The
system uses the dual polarisation dipole like antennas which are
omidirectional patterned. The front end electonics (FEE) are
configured in a printed circuit board (PCB) which makes it easy for
them to be mounted on the supporting structure of the antennas. From
the FEE PCB, a coaxial cable sends the signal through to the bias tee
which extracts both the RF and the DC without any degradation.

The high pass and the low pass filter rejects the low frequency
signals and high frequency signals respectively. The signal is then
amplified by a $\approx$20 dB amplifier which then send the amplified
signals to the Smart Network ADC Processor (SNAP) board which does the
readouts and does a series of processing step. The raspberry pi
interacts with the SNAP board for data storage.
